---
output:
    md_document:
      variant: markdown_github
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "tools/README-",
  warning = FALSE
)
```

# dubois: From DuBois Challenge 2022, an area plot in 'ggplot2'

<img align="left" src="https://github.com/IcaroBernardes/dubois/blob/master/img/dubois%20(2).png?raw=true" alt="logo" width="140"> 
       
[ggplot2, by Hadley Wickham, ](https://ggplot2.tidyverse.org/) is an excellent package for data visualization in R. From DuBois Challenge 2022, i developed an area plot in ggplot2. It shows the percentage of blacks and whites in managerial positions 

The development inspiration came from the #DuBoisChallenge2022 and the dissemination of SER (International Seminar on Statistics with R).

## Installation and loading

- Install [GitHub](https://github.com/IcaroBernardes/dubois) as follow: 
    
   
```{r, eval = FALSE}
# Install
if(!require(devtools)) install.packages("devtools")
devtools::install_github("IcaroBernardes/dubois")
```

## Load
     
```{r dubois, warning=FALSE}
library(dubois)

df <- dubois::managers
dubois::db_area()
```

## Blog posts
   
- Icaro BSC [Twitter](https://twitter.com/IcaroBSC/status/1501323176088780800)

